\myTitle

### 2024-02-05 body-text-of-paper.tex
Add a and b to Fig 4, plus minor edits to discussion

As expected, the perceived ability to estimate $q_A$ with ADMIXTURE was higher
for larger values of $L$ and for smaller values of $N$ (Figure~\ref{fig:bias-sims}).
%%%
\begin{figure*}
\newcommand{\biassimscap}{\footnotesize ADMIXTURE estimates of $q_A$ as described in
{\em An introductory motivating example}. In these results, the apparent ability to estimate $q_A$
is a bias resulting from the use of sampling with replacement to simulate new, admixed genotypes to
test in ADMIXTURE.  In each figure, the different columns represent different numbers of markers
from 10 to 100,000, while different rows represent different original sample sizes, $N$, taken. Colors
of the boxplots indicate how many new individuals, $n$, of each $q_A$ value were simulated during each
replicate.}
\includegraphics[width=0.96\textwidth]{figures/bias-sims-unsup-and-sup.pdf}
\caption[\biassimscap]{\biassimscap}
\label{fig:bias-sims}
\end{figure*}
%%%
It is interesting to note
that, for numbers of loci,  $L$, that are 100 (or smaller) the effect is observed only when
sample size, $N$, is as small as 25---and even then the effect is slight.  However, when the
number of markers increases to 100,000---values that are becoming commonplace with the availability of chip-
or sequencing-based approaches---it is apparent that the sampling-with-replacement approach
induces an extreme bias.  With 100,000 markers, even if sample sizes ($N$) are as large as 250 individuals,
using na\"{i}ve simulations improperly indicates that admixture fractions of individuals can be
accurately estimated, even when there are no genetic differences, whatsoever between the populations that
samples $A$ and $B$ are drawn.

@@

Here, we present \gscramble{}, a simulation approach for creating biologically informed individual 
genotypes of different hybrid classes. Two integral features of \gscramble{} are: 
1) alleles are sampled from populations without replacement and 
2) alleles are segregated based on species-specific recombination rates. 
Our results show that both 
of these features are especially important for accurately reflecting empirical data from large genetic 
marker sets (thousands of markers), 
which are common from next generation sequencing methods. Sampling alleles without 
replacement, and thereby preserving the genetic differences (or lack thereof) of populations is 
essential for avoiding the issue of RISPI---an issue that is exacerbated as the number of 
alleles sampled for an individual increases. Additionally, we show the importance of accounting for 
the physical linkage of markers when large marker sets are used and that treating loci as 
independent results in erroneously reduced variation in the estimation of individuals' admixture 
fractions.

>>>>

As expected, the perceived ability to estimate $q_A$ with ADMIXTURE was higher
for larger values of $L$ and for smaller values of $N$ (Figure~\ref{fig:bias-sims}).
%%%
\begin{figure*}
\newcommand{\biassimscap}{\footnotesize ADMIXTURE estimates of $q_A$ as described in
{\em An introductory motivating example}. In these results, the apparent ability to estimate $q_A$
is a bias resulting from the use of sampling with replacement to simulate new, admixed genotypes to
test in ADMIXTURE.  ({\bf a}) Results from the supervised analysis in ADMIXTURE, where 
"ref-2" and "ref-1" show the $Q$-values estimated by ADMIXTURE for the reference samples
(even though they are treated by the program as being of known origin). ({\bf b}) Results for the
unsupervised analysis in ADMIXTURE. In both {\bf a} and {\bf b}, the different columns represent different numbers of markers
from 10 to 100,000, while different rows represent different original sample sizes, $N$, taken. Colors
of the boxplots indicate how many new individuals, $n$, of each $q_A$ value were simulated during each
replicate.}
\includegraphics[width=0.96\textwidth]{figures/bias-sims-unsup-and-sup.pdf}
\caption[\biassimscap]{\biassimscap}
\label{fig:bias-sims}
\end{figure*}
%%%
It is interesting to note
that, for numbers of loci,  $L$, that are 100 (or smaller) the effect is observed only when
sample size, $N$, is as small as 25---and even then the effect is slight.  However, when the
number of markers increases to 100,000---values that are becoming commonplace with the availability of chip-
or sequencing-based approaches---it is apparent that the sampling-with-replacement approach
induces an extreme bias.  With 100,000 markers, even if sample sizes ($N$) are as large as 250 individuals,
using na\"{i}ve simulations improperly indicates that admixture fractions of individuals can be
accurately estimated, even when there are no genetic differences, whatsoever between the populations that
samples $A$ and $B$ are drawn.

@@

Here, we present \gscramble{}, a simulation approach for creating biologically informed individual 
genotypes of different hybrid classes. Two integral features of \gscramble{} are: 
1) alleles are sampled from populations without replacement and 
2) alleles are segregated based on species-specific recombination rates. 
Our results show that both 
of these features are especially important for accurately reflecting empirical data from large genetic 
marker sets (thousands of markers), 
which are common from  both custom SNP-chip genotyping and next generation sequencing methods. Sampling alleles without 
replacement, and thereby preserving the genetic differences (or lack thereof) of populations is 
essential for avoiding RISPI---an issue that is exacerbated as the number of 
alleles sampled for an individual increases. Additionally, we show the importance of accounting for 
the physical linkage of markers when large marker sets are used and that treating loci as 
independent results in erroneously reduced variation in the admixture 
fractions of simulated individuals.
